Supplementary Figure 2a

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
re-running Rmds after addition of suppFig3

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure2d"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure2d"][[1]]

@@

url <- fileMap(type = "rds")["suppFigure2d"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(
      y = 1:length(pull(., level)),
      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
    )

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure3d"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3d"][[1]]

@@

url <- fileMap(type = "rds")["suppFigure3d"][[1]]
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(
      y = 1:length(pull(., level)),
      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
    )

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
# ggsave(
#   plot = g,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
re-running Rmds after addition of suppFig3

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure2e"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure2e"][[1]]

@@

#splice junctions
url <- fileMap(type = "rds")["suppFigure2e"][[1]]
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])

ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)

>>>>

```{r}
nrCellLinesDown <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "txt")["suppFigure3e"][[1]]

@@

cellLinesInFinal <- function() {
  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
  url <- fileMap(type = "rds")["suppFigure3e"][[1]]

@@

#splice junctions
url <- fileMap(type = "rds")["suppFigure3e"][[1]]
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3e"][[1]])
# ggsave(
#   plot = g,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
re-running Rmds after addition of suppFig3

url <- fileMap(type = "rds")["figure2d"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

>>>>

url <- fileMap(type = "rds")["figure2c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2c"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
re-running Rmds after addition of suppFig3

url <- fileMap(type = "rds")["figure2e"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

>>>>

url <- fileMap(type = "rds")["figure2d"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
# ggsave(
#    plot = figure,
#    filename = path,
#    device = cairo_pdf,
#    height = 60,
#    width = 83,
#    units = "mm"
# )
```

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
re-running Rmds after addition of suppFig3

url <- fileMap(type = "rds")["suppFigure2b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 43,
#  units = "mm"
# )
```

>>>>

url <- fileMap(type = "rds")["suppFigure3b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3b"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#    device = cairo_pdf,
#   height = 60,
#    width = 43,
#   units = "mm"
# )
```

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
re-running Rmds after addition of suppFig3

url <- fileMap(type = "rds")["suppFigure2c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 43,
  units = "mm"
)
```

>>>>

url <- fileMap(type = "rds")["suppFigure3c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3c"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 43,
#   units = "mm"
# )
```

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
re-running Rmds after addition of suppFig3

url <- fileMap(type = "rds")["suppFigure2a"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 130,
#  units = "mm"
# )
```

>>>>

url <- fileMap(type = "rds")["suppFigure3a"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3a"][[1]])
# ggsave(
#   plot = figure,
#    filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 130,
#   units = "mm"
# )
```
